---
title: "Survey Two - Image Recognition - Data Cleaning"
author: "Hari VS"
Date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document: default
---

```{r warning=FALSE}
library(tidyverse) #for tidyr and new tidy version coding
library(dplyr) #for pipe usage
library(lubridate) #to handle date and time
```

# _____________________________________________________________________________
### RAW DATA OBTAINED FROM PROLIFIC THROUGH SURVEY
### THIS FILE CONTAINS ONLY THE CLEANING CODE

### DATA IS CLEANED AND SAVED IN MULTIPLE FORMATS

####    1. EACH PERSON IS AN OBSERVATION
            1A. AVERAGED ACROSS ALL IMAGES
            1B. AVERAGED ACROSS PLANTS ONLY IMAGES
            1C. AVERAGED ACROSS ANIMALS ONLY IMAGES
# _____________________________________________________________________________

```{r}
# import raw data from Qualtrics
raw_data <- read_csv("Datasets/study_data.csv")

#copying data so originial is left untouched
data_person <- raw_data 

#Removing first two unwanted rows. Duplicates for column names
data_person <- data_person[-c(1,2),]

#Converting class of the timestamps
data_person$StartDate <-  as_datetime(data_person$StartDate)

#started collecting data on 2/11/21 at 6:30 PM
data_person <- 
  filter(data_person, StartDate >= #select cells
as.POSIXct("2021-02-11 18:30:00", #that has timestamps past 6:30 PM on 02/11/21
tz = "UTC")) %>% #timestamps are in Mountrain TimeZone
  filter(Finished == "True") #removing incomplete surveys

#Removing unwanted columns
data_person <- select(data_person, -c("EndDate": "Progress","RecordedDate", 
                      "RecipientLastName" : "UserLanguage", "Comments",
                      "mTurkCode")) #Specifying column names

# remove unused factor levels
data_person <- droplevels(data_person)

# convert to tibble
data_person <- as_tibble(data_person)

#Removing columns that has NAs for all cells
all_na <- function(x){
  any(!is.na(x)) #anything is that not NA.
#write the names of the columns.
} 

#Applying the all_na funtion to data_person tibble
data_person <- data_person[, #chossing columns from the data frame
                           which( #mentioning which columns
                             unlist( #drop the one that follows lapply
                               lapply(data_person,all_na)))]
                               #lapply tells to apply all_na function

#Removing more unwanted columns
data_person <- data_person %>% 
  select(-contains("Click")) #These columns are not needed
#These columns recorded the first click and last click time (in seconds) for
#every stimuli. It also recorded click counts for all.

#Removing Hannah from dataset - 
#Survey Preview done by peer during data collection
data_person <- data_person[data_person$`P-ID` != "Hannah",]
  
```

#### Age
```{r}
#convert to numeric
data_person$Year_born <- as.numeric(data_person$Year_born)

# calculate age
data_person$age <- 2020 - data_person$Year_born #numeric class
```

#### Education
```{r}
# Creating dummy variable for EDUCATION
data_person$college <- #4-year degree or higher = 1, else = 0.
  #case_when: if response is equal to "x", assign "y"
  case_when(
    data_person$Education == "Graduate degree" ~ 1,
    data_person$Education == "4 year degree" ~ 1,
    data_person$Education == "2 year degree" ~ 0,
    data_person$Education == "Some college" ~ 0,
    data_person$Education == "High School" ~ 0,
    data_person$Education == "Less than high school" ~ 0)
```

#### Gender
```{r}
#Creating dummy variable for Gender. Male = 1, else = 0.
data_person$male_num <- ifelse(data_person$Gender == "Male",1,0)
```

#### AI Trustworthiness Rating
```{r}
# AI TRUST - numeric version
data_person$AI_trust_num <- case_when( 
  #case_when: if response is equal to "x", assign "y"
  data_person$AI_trust == "Very untrustworthy" ~ 1,
  data_person$AI_trust == "Somewhat untrustworthy" ~ 2,
  data_person$AI_trust == "Neither untrustworthy nor trustworthy" ~ 3,
  data_person$AI_trust == "Somewhat trustworthy" ~ 4,
  data_person$AI_trust == "Very trustworthy" ~ 5,
)
```

#### Survey Task Difficulty Rating
```{r}
# TASK DIFFICULTY - numeric version
data_person$Task_diff_num <- case_when(
  #case_when: if response is equal to "x", assign "y"
  data_person$Task_diff == "Extremely easy" ~ 1,
  data_person$Task_diff == "Somewhat easy" ~ 2,
  data_person$Task_diff == "Neither easy nor difficult" ~ 3,
  data_person$Task_diff == "Somewhat difficult" ~ 4,
  data_person$Task_diff == "Extremely difficult" ~ 5,
)
```

#### Animals Domian Knowledge Self-Rating
```{r}
#Domain Knowledge - Animals - Numeric
data_person$Dmn_know_a_num <- case_when(
  #case_when: if response is equal to "x", assign "y"
  data_person$Dmn_know_a == "Extremely well" ~ 1,
  data_person$Dmn_know_a == "Very well" ~ .8,
  data_person$Dmn_know_a == "Moderately well" ~ .6,
  data_person$Dmn_know_a == "Somewhat well" ~ .4,
  data_person$Dmn_know_a == "Slightly well" ~ .2,
  data_person$Dmn_know_a == "Not well at all" ~ 0
)
```

#### Plants Domain Knowledge Self-Rating
Domain knowledge ratings of plants are represented in binary terms since
approximately half the participants rated they had no domain knowledge in
identifying plants.
```{r}
#Domain knowledge - Plants - Binary
data_person$Dmn_know_p_num <- case_when(
  #case_when: if response is equal to "x", assign "y"
  data_person$Dmn_know_p == "Extremely well" ~ 1,
  data_person$Dmn_know_p == "Very well" ~ .8,
  data_person$Dmn_know_p == "Moderately well" ~ .6,
  data_person$Dmn_know_p == "Somewhat well" ~ .4,
  data_person$Dmn_know_p == "Slightly well" ~ .2,
  data_person$Dmn_know_p == "Not well at all" ~ 0
)
```

#### Attention Checks
```{r}
#Howler Monkey is the correct response to the first attention check.
data_person$atn_ch1_num <- #creating a new column for attention check 1.
  ifelse(data_person$atn_ch1 == "Howler Monkey",1, 0)

#Attention check asking how many recommendations they get for each image. "6"
data_person$atn_ch2_num <-  #creating column for attention check 2.
  ifelse(data_person$atn_ch2 == 6,1, 0) #If they chose 6, apply 1 (correct),
                                        #else 0.

#Attention check mentions to pick "Howler Monkey".
data_person$atn_ch3_num <- #creating column for attention check 3.
  ifelse(data_person$atn_ch3 == "Howler Monkey",1,0)

# sum to indicate total attention checks correctly responded to
data_person$atn_ch_sum <- rowSums(data_person %>% #summing three columns
                                        select(atn_ch1_num:atn_ch3_num))

# binary indicator for passing all attention checks.
data_person$atn_ch <- #if they passed all three checks, assign 1, else 0.
  ifelse(data_person$atn_ch1_num == 1 &
           data_person$atn_ch2_num == 1 &
           data_person$atn_ch3_num == 1,1, 0)
```

#### Tidying data to help reshaping the tibble
Storing column names alphabetically in a vector so that it can be rearranged in
a desired manner for analysis. Chunk below is for *Stimuli Responses*.  
```{r}
#Rearranging columns - responses to no AI stimuli.
no_AI_resp <- data_person %>% #store in a vector
  select(contains("no_AI_resp")) %>% 
  colnames() %>% #choose columns with NO_AI_resp in the name
  sort() #arrange alphabetically

#Rearranging columns - responses to AI_nobar stimuli.
AI_nobar_resp <- data_person %>% #store in a vector
  select(contains("AI_nobar_resp")) %>% 
  colnames() %>% #choose columns with AI_nobar_resp in the name
  sort() #arrange alphabetically

#Rearranging columns - responses to AI_bar stimuli.
AI_bar_resp <- data_person %>% #store in a vector
  select(contains("AI_bar_resp")) %>% 
  colnames() %>% #choose columns with AI_bar_resp in the name
  sort() #arrange alphabetically
```

Storing column names into vectors for *confidence ratings*.  
```{r}
#Rearranging columns - responses to no AI Confidence.
no_AI_conf <- data_person %>%
  select(contains("no_AI_conf")) %>% 
  colnames() %>%
  sort()

#Rearranging columns - responses to AI_nobar Confidence.
AI_nobar_conf <- data_person %>%
  select(contains("AI_nobar_conf")) %>% 
  colnames() %>%
  sort()

#Rearranging columns - responses to AI_bar Confidence.
AI_bar_conf <- data_person %>%
  select(contains("AI_bar_conf")) %>% 
  colnames() %>%
  sort()
```

Storing column names into vectors for *time taken per image*.  
```{r}
#Rearranging columns - time taken in no AI condition.
no_AI_time <- data_person %>%
  select(contains("no_AI_time")) %>% 
  colnames() %>%
  sort()

#Rearranging columns - time taken in AI_nobar condition.
AI_nobar_time <- data_person %>%
  select(contains("AI_nobar_time")) %>% 
  colnames() %>%
  sort()

#Rearranging columns - time taken in AI_bar condition.
AI_bar_time <- data_person %>%
  select(contains("AI_bar_time")) %>% 
  colnames() %>%
  sort()
```

Storing column names into vectors for *AI Usefulness ratings*.  
```{r}
#Rearranging columns - Usefulness rating in AI_nobar condition.
AI_nobar_use <- data_person %>%
  select(contains("AI_nobar_use")) %>% 
  colnames() %>%
  sort()

#Rearranging columns - Usefulness rating in AI_bar condition.
AI_bar_use <- data_person %>%
  select(contains("AI_bar_use")) %>% 
  colnames() %>%
  sort()
```




#### Reshaping Data frame 
```{r}
data_person <- data_person %>%
  select(no_AI_resp, AI_nobar_resp, AI_bar_resp, no_AI_conf, AI_nobar_conf,
         AI_bar_conf, no_AI_time, AI_nobar_time, AI_bar_time, AI_nobar_use,
         AI_bar_use, #arranging the dataframe by using the vectors
         Group, everything()) #mentioning everything else to remain untouched.

```

#### Time taken per stimuli
```{r}
#converting to numeric
time_chr_to_num <- function(x){
  as.numeric(x)
}

#Applying function to all stimulus' time recordings
data_person <- data_person %>% #choosing tibble
  mutate_at(.vars = vars(`Barc_no_AI_time_Page Submit` : 
                           `Zuch_AI_bar_time_Page Submit`), 
            #.vars - mentioning the column names to mutate
            .funs = funs(time_chr_to_num)) #applying the function
```

#### Stimuli Correct Responses
```{r}
source("stimuli_response_coding.R") #code is included in a separate R file.
```

#### Confidence ratings for each stimuli
```{r}
#creating a function to convert chr to numerics.
conf_num <- function(x){
case_when(  
  #case_when: if response is equal to "x", assign "y"
  x == "Not confident at all (0% - 20%)" ~ 0,
  x == "Slightly confident (21% - 40%)" ~ .2,
  x == "Moderately confident (41% - 60%)" ~ .4,
  x == "Very confident    (61% - 80%)" ~ .6,
  x == "Extremely confident (81% - 99%)" ~ .8,
  x ==  "Absolutely confident (100%)" ~ 1)}

#applying the function in tibble.
data_person <- data_person %>% #choosing tibble
  mutate_at(.vars = vars(Barc_no_AI_conf: Zuch_AI_bar_conf), 
            #.vars - mentioning the column names to mutate
            .funs = funs(conf_num)) #applying the function

#converting to numeric
conf_chr_to_num <- function(x){
  as.numeric(x)
}

#applying function to all confidence responses
data_person <- data_person %>% #choosing tibble
  mutate_at(.vars = vars(Barc_no_AI_conf : Zuch_AI_bar_conf), 
            #.vars - mentioning the column names to mutate
            .funs = funs(conf_chr_to_num)) #applying the function
```

#### AI usefulness ratings
```{r}
#Creating a function for AI usefulness columns.
AI_use_num <- function(x){
  case_when(  
  #case_when: if response is equal to "x", assign "y"
  x == "Extremely useful" ~ 1,
  x == "Very useful" ~ .8,
  x == "Moderately useful" ~ .6,
  x == "Somewhat useful" ~ .4,
  x == "Slightly useful" ~ .2,
  x == "Not useful at all" ~ 0)}

#applying function - converting them to numbers
data_person <- data_person %>% #choosing tibble
  mutate_at(.vars = vars(Barc_AI_nobar_use:Zuch_AI_bar_use),
            #.vars - mentioning the column names to mutate
            .funs = funs(AI_use_num,)) #applying the function

```

# Total time taken
```{r}
#Converting to numeric
data_person$`Duration (in seconds)` <- as.numeric(
                                       data_person$`Duration (in seconds)`
                                       )
```

# #############################################################################
# #############################################################################
# _____________________________________________________________________________
#### END OF GENERAL CLEANING OF VARIABLES
#### ALL FOLLOWING CODE CHUNKS BELOW ARE FOR CREATING THE MULITPLE DATASETS
# _____________________________________________________________________________
# #############################################################################
# #############################################################################








# Separating Plants and Animals stimulus. 
Creating two data frames that will separate the plants and animals stimulus so
that data can be analyzed how the performance in two different domains.

```{r}
plants_person <- data_person %>%
  select(contains(c("Cherry", "CPoppy", "Cyclmn", "Eldb", "FlyOrc", "Frag",
                    "Gazn", "Hen", "Huis", "Log", "Mulb", "NZB", "Pars",
                    "Phaius", "Polyp", "Pomg", "Rseed", "Shal", "Zuch")), 
         c("Group":"atn_ch"))


animals_person <- data_person %>%
  select(-contains(c("Cherry", "CPoppy", "Cyclmn", "Eldb", "FlyOrc", "Frag",
                    "Gazn", "Hen", "Huis", "Log", "Mulb", "NZB", "Pars",
                    "Phaius", "Polyp", "Pomg", "Rseed", "Shal", "Zuch")), 
         c("Group":"atn_ch"))
```

# #############################################################################
# #############################################################################
# _____________________________________________________________________________
#### TIDYING FOR PLANTS DATASET
# _____________________________________________________________________________
# #############################################################################
# #############################################################################

#### Tidying data to help reshaping the tibble
Storing column names alphabetically in a vector so that it can be rearranged in
a desired manner for analysis. Chunk below is for *Stimuli Responses*.  
```{r}
#Rearranging columns - responses to no AI stimuli.
no_AI_resp_p <- plants_person %>% #store in a vector
  select(contains("no_AI_resp")) %>% 
  colnames() %>% #choose columns with NO_AI_resp_p in the name
  sort() #arrange alphabetically

#Rearranging columns - responses to AI_nobar stimuli.
AI_nobar_resp_p <- plants_person %>% #store in a vector
  select(contains("AI_nobar_resp")) %>% 
  colnames() %>% #choose columns with AI_nobar_resp_p in the name
  sort() #arrange alphabetically

#Rearranging columns - responses to AI_bar stimuli.
AI_bar_resp_p <- plants_person %>% #store in a vector
  select(contains("AI_bar_resp")) %>% 
  colnames() %>% #choose columns with AI_bar_resp_p in the name
  sort() #arrange alphabetically
```

Storing column names into vectors for *confidence ratings*.  
```{r}
#Rearranging columns - responses to no AI Confidence.
no_AI_conf_p <- plants_person %>%
  select(contains("no_AI_conf")) %>% 
  colnames() %>%
  sort()

#Rearranging columns - responses to AI_nobar Confidence.
AI_nobar_conf_p <- plants_person %>%
  select(contains("AI_nobar_conf")) %>% 
  colnames() %>%
  sort()

#Rearranging columns - responses to AI_bar Confidence.
AI_bar_conf_p <- plants_person %>%
  select(contains("AI_bar_conf")) %>% 
  colnames() %>%
  sort()
```

Storing column names into vectors for *time taken per image*.  
```{r}
#Rearranging columns - time taken in no AI condition.
no_AI_time_p <- plants_person %>%
  select(contains("no_AI_time")) %>% 
  colnames() %>%
  sort()

#Rearranging columns - time taken in AI_nobar condition.
AI_nobar_time_p <- plants_person %>%
  select(contains("AI_nobar_time")) %>% 
  colnames() %>%
  sort()

#Rearranging columns - time taken in AI_bar condition.
AI_bar_time_p <- plants_person %>%
  select(contains("AI_bar_time")) %>% 
  colnames() %>%
  sort()
```

Storing column names into vectors for *AI Usefulness ratings*.  
```{r}
#Rearranging columns - Usefulness rating in AI_nobar condition.
AI_nobar_use_p <- plants_person %>%
  select(contains("AI_nobar_use")) %>% 
  colnames() %>%
  sort()

#Rearranging columns - Usefulness rating in AI_bar condition.
AI_bar_use_p <- plants_person %>%
  select(contains("AI_bar_use")) %>% 
  colnames() %>%
  sort()
```

#### Reshaping Data frame 
```{r}
plants_person <- plants_person %>%
  select(no_AI_resp_p, AI_nobar_resp_p, AI_bar_resp_p, no_AI_conf_p, AI_nobar_conf_p,
         AI_bar_conf_p, no_AI_time_p, AI_nobar_time_p, AI_bar_time_p, AI_nobar_use_p,
         AI_bar_use_p, #arranging the dataframe by using the vectors
         Group, everything()) #mentioning everything else to remain untouched.

```

# _____________________________________________________________________________
### CLEANING FOR PLANTS BY PERSON DATASET 
### EACH OBSERVATION IS ONE PERSON
# _____________________________________________________________________________

#### Averaging across images for plants data set
Creating/Finalizing the data set where each observation is a person. Chunk below
creates all the *AI vs No-AI averages* across images.  
```{r}
#Average Accuracy no-AI
plants_person$avg_no_AI_acc <- (rowSums(plants_person %>% 
            #summing columns for all images in NO AI condition
            select(Cherry_no_AI_resp : Zuch_no_AI_resp), na.rm = TRUE))/19
            #Divided by 19 since there are 19 stimulus in the experiment

#Average Accuracy AI
plants_person$avg_AI_acc <- (rowSums(plants_person %>%
            select(Cherry_AI_nobar_resp : Zuch_AI_bar_resp), na.rm = TRUE))/19

#Average Confidence no-AI
plants_person$avg_no_AI_conf <- (rowSums(plants_person %>%
            select(Cherry_no_AI_conf : Zuch_no_AI_conf), na.rm = TRUE))/19

#Average Confidence AI
plants_person$avg_AI_conf <- (rowSums(plants_person %>%
            select(Cherry_AI_nobar_conf : Zuch_AI_bar_conf), na.rm = TRUE))/19

#Average Time per image no-AI
plants_person$avg_no_AI_time <- (rowSums(plants_person %>%
            select(`Cherry_no_AI_time_Page Submit` : 
                     `Zuch_no_AI_time_Page Submit`), na.rm = TRUE))/19

#Average Time per image AI
plants_person$avg_AI_time <- (rowSums(plants_person %>%
            select(`Cherry_AI_nobar_time_Page Submit` : 
                     `Zuch_AI_bar_time_Page Submit`), na.rm = TRUE))/19

#Placeholder for AI usefulness rating in No-AI condition.
plants_person$avg_no_AI_use <- NA

#Average AI usefulness rating.
plants_person$avg_AI_use <- (rowSums(plants_person %>%
            select(Cherry_AI_nobar_use : Zuch_AI_bar_use), na.rm = TRUE))/19
```

#### Data set containing only AI vs NO-AI columns
```{r}
#Each observation is a person. No mixed effects to be modeled with this dataset
plants_by_person <- select(plants_person, c("Group","StartDate":"ResponseId", "PROLIFIC_PID" : "avg_AI_use"))
```

#### Stacking columns - all accuracy in one column, all conf in one column...
```{r}
plants_by_person <- cbind(plants_by_person %>% #choosing dataset
                     select(1:18), #mentioning columns to be left untouched.
                   stack(plants_by_person %>% #makes dataset from wide to long
                           select(avg_no_AI_acc:avg_AI_acc)), #choosing cols.
                   stack(plants_by_person %>%
                           select(avg_no_AI_conf:avg_AI_conf)),
                   stack(plants_by_person %>%
                           select(avg_no_AI_time:avg_AI_time)),
                   stack(plants_by_person %>%
                           select(avg_no_AI_use:avg_AI_use)))
```


```{r}
#Providing names for the newly stacked columns
colnames(plants_by_person)[19:26] <- c("accuracy", "exp_condition", 
                                "confidence", "conf_name",
                                "time_taken", "time_name",
                                "AI_use", "AI_use_name")

#Since they are repeated, columns are removed
plants_by_person <- plants_by_person %>%
  select(-contains("name"))
```


```{r}
#Creating a column that indicates if the response was for No-AI or AI condition
plants_by_person$AI <- ifelse(plants_by_person$exp_condition == "avg_AI_acc", 1, 0)

#Column to indicate if uncertainty information was provided
plants_by_person$bar <- ifelse(plants_by_person$AI == 1 & #both statements must be true
                          plants_by_person$Group == "AI_bars" ,1, 0)
#if AI information was provied & they were placed in AI_bars condition, then 1.
```


```{r}
#removing columns that are not necessary anymore
plants_by_person <- select(plants_by_person, -c("Group":"Finished","PROLIFIC_PID", "atn_ch1_num":"atn_ch_sum", "exp_condition"))
```


#### Exporting cleaned *by_person averages* data set
```{r}
#2 Each observation is one person for plants
write.csv(plants_by_person,file="Datasets/Data_cleaned_plants_person.csv")
#Use only for t-tests and linear regressions with no mixed effects.
#This dataset will be used for the first part of the analysis.
```

# #############################################################################
# #############################################################################
# _____________________________________________________________________________
### END OF CLEANING FOR PLANTS BY PERSON DATASET - ONLY PLANTS
### EACH OBSERVATION IS ONE PERSON
# _____________________________________________________________________________
# #############################################################################
# #############################################################################


# _____________________________________________________________________________
### CLEANING FOR ANIMALS BY PERSON DATASET 
### EACH OBSERVATION IS ONE PERSON
# _____________________________________________________________________________

#### Averaging across images for animals data set
Creating/Finalizing the data set where each observation is a person. Chunk below
creates all the *AI vs No-AI averages* across images. 

```{r}
#Average Accuracy no-AI
animals_person$avg_no_AI_acc <- (rowSums(animals_person %>% 
            #summing columns for all images in NO AI condition
            select(Barc_no_AI_resp : Smonk_no_AI_resp), na.rm = TRUE))/13
            #Divided by 13 since there are 13 stimulus in the experiment

#Average Accuracy AI
animals_person$avg_AI_acc <- (rowSums(animals_person %>%
            select(Barc_AI_nobar_resp : Smonk_AI_bar_resp), na.rm = TRUE))/13

#Average Confidence no-AI
animals_person$avg_no_AI_conf <- (rowSums(animals_person %>%
            select(Barc_no_AI_conf : Smonk_no_AI_conf), na.rm = TRUE))/13

#Average Confidence AI
animals_person$avg_AI_conf <- (rowSums(animals_person %>%
            select(Barc_AI_nobar_conf : Smonk_AI_bar_conf), na.rm = TRUE))/13

#Average Time per image no-AI
animals_person$avg_no_AI_time <- (rowSums(animals_person %>%
            select(`Barc_no_AI_time_Page Submit` : 
                     `Smonk_no_AI_time_Page Submit`), na.rm = TRUE))/13

#Average Time per image AI
animals_person$avg_AI_time <- (rowSums(animals_person %>%
            select(`Barc_AI_nobar_time_Page Submit` : 
                     `Smonk_AI_bar_time_Page Submit`), na.rm = TRUE))/13

#Placeholder for AI usefulness rating in No-AI condition.
animals_person$avg_no_AI_use <- NA

#Average AI usefulness rating.
animals_person$avg_AI_use <- (rowSums(animals_person %>%
            select(Barc_AI_nobar_use : Smonk_AI_bar_use), na.rm = TRUE))/13
```

#### Data set containing only AI vs NO-AI columns
```{r}
#Each observation is a person. No mixed effects to be modeled with this dataset
animals_by_person <- select(animals_person, c("Group","StartDate":"ResponseId", "PROLIFIC_PID" : "avg_AI_use"))
```

#### Stacking columns - all accuracy in one column, all conf in one column...
```{r}
animals_by_person <- cbind(animals_by_person %>% #choosing dataset
                     select(1:18), #mentioning columns to be left untouched.
                   stack(animals_by_person %>% #makes dataset from wide to long
                           select(avg_no_AI_acc:avg_AI_acc)), #choosing cols.
                   stack(animals_by_person %>%
                           select(avg_no_AI_conf:avg_AI_conf)),
                   stack(animals_by_person %>%
                           select(avg_no_AI_time:avg_AI_time)),
                   stack(animals_by_person %>%
                           select(avg_no_AI_use:avg_AI_use)))
```


```{r}
#Providing names for the newly stacked columns
colnames(animals_by_person)[19:26] <- c("accuracy", "exp_condition", 
                                "confidence", "conf_name",
                                "time_taken", "time_name",
                                "AI_use", "AI_use_name")

#Since they are repeated, columns are removed
animals_by_person <- animals_by_person %>%
  select(-contains("name"))
```


```{r}
#Creating a column that indicates if the response was for No-AI or AI condition
animals_by_person$AI <- ifelse(animals_by_person$exp_condition == "avg_AI_acc", 1, 0)

#Column to indicate if uncertainty information was provided
animals_by_person$bar <- ifelse(animals_by_person$AI == 1 & #both statements must be true
                          animals_by_person$Group == "AI_bars" ,1, 0)
#if AI information was provied & they were placed in AI_bars condition, then 1.
```


```{r}
#removing columns that are not necessary anymore
animals_by_person <- select(animals_by_person, -c("Group":"Finished","PROLIFIC_PID", "atn_ch1_num":"atn_ch_sum", "exp_condition"))
```


#### Exporting cleaned *by_person averages* data set
```{r}
#4 Each observation is one person for animals stimuli
write.csv(animals_by_person,file="Datasets/Data_cleaned_animals_person.csv")
#Use only for t-tests and linear regressions with no mixed effects.
#This dataset will be used for the first part of the analysis.
```

# #############################################################################
# #############################################################################
# _____________________________________________________________________________
### END OF CLEANING FOR ANIMALS BY PERSON DATASET - ONLY ANIMALS
### EACH OBSERVATION IS ONE PERSON
# _____________________________________________________________________________
# #############################################################################
# #############################################################################

#### Averaging across images - BOTH PLANTS AND ANIMALS
Creating/Finalizing the data set where each observation is a person. Chunk below
creates all the *AI vs No-AI averages* across images.  

```{r}
#Average Accuracy no-AI
data_person$avg_no_AI_acc <- (rowSums(data_person %>% 
            #summing columns for all images in NO AI condition
            select(Barc_no_AI_resp : Zuch_no_AI_resp), na.rm = TRUE))/32
            #Divided by 32 since there are 32 stimulus in the experiment

#Average Accuracy AI
data_person$avg_AI_acc <- (rowSums(data_person %>%
            select(Barc_AI_nobar_resp : Zuch_AI_bar_resp), na.rm = TRUE))/32

#Average Confidence no-AI
data_person$avg_no_AI_conf <- (rowSums(data_person %>%
            select(Barc_no_AI_conf : Zuch_no_AI_conf), na.rm = TRUE))/32

#Average Confidence AI
data_person$avg_AI_conf <- (rowSums(data_person %>%
            select(Barc_AI_nobar_conf : Zuch_AI_bar_conf), na.rm = TRUE))/32

#Average Time per image no-AI
data_person$avg_no_AI_time <- (rowSums(data_person %>%
            select(`Barc_no_AI_time_Page Submit` : 
                     `Zuch_no_AI_time_Page Submit`), na.rm = TRUE))/32

#Average Time per image AI
data_person$avg_AI_time <- (rowSums(data_person %>%
            select(`Barc_AI_nobar_time_Page Submit` : 
                     `Zuch_AI_bar_time_Page Submit`), na.rm = TRUE))/32

#Placeholder for AI usefulness rating in No-AI condition.
data_person$avg_no_AI_use <- NA

#Average AI usefulness rating.
data_person$avg_AI_use <- (rowSums(data_person %>%
            select(Barc_AI_nobar_use : Zuch_AI_bar_use), na.rm = TRUE))/32
```

#### Data set containing only AI vs NO-AI columns
```{r}
#Each observation is a person. No mixed effects to be modeled with this dataset
by_person <- select(data_person, c("Group","StartDate":"ResponseId", "PROLIFIC_PID" : "avg_AI_use"))
```


```{r}
#for within-subjects correlation matrix
within_corr <- select(by_person, c("Group", "ResponseId", "age": "Dmn_know_p_num", "atn_ch": "avg_AI_time", "avg_AI_use"))

within_corr$Group <- ifelse(within_corr$Group == "AI_bars",1,0)

#exporting as .csv file
write.csv(within_corr,file="Datasets/corr_csv_within.csv")
```


#### Stacking columns - all accuracy in one column, all conf in one column...
```{r}
by_person <- cbind(by_person %>% #choosing dataset
                     select(1:18), #mentioning columns to be left untouched.
                   stack(by_person %>% #makes dataset from wide to long
                           select(avg_no_AI_acc:avg_AI_acc)), #choosing cols.
                   stack(by_person %>%
                           select(avg_no_AI_conf:avg_AI_conf)),
                   stack(by_person %>%
                           select(avg_no_AI_time:avg_AI_time)),
                   stack(by_person %>%
                           select(avg_no_AI_use:avg_AI_use)))
```


```{r}
#Providing names for the newly stacked columns
colnames(by_person)[19:26] <- c("accuracy", "exp_condition", 
                                "confidence", "conf_name",
                                "time_taken", "time_name",
                                "AI_use", "AI_use_name")

#Since they are repeated, columns are removed
by_person <- by_person %>%
  select(-contains("name"))
```


```{r}
#Creating a column that indicates if the response was for No-AI or AI condition
by_person$AI <- ifelse(by_person$exp_condition == "avg_AI_acc", 1, 0)

#Column to indicate if uncertainty information was provided
by_person$bar <- ifelse(by_person$AI == 1 & #both statements must be true
                          by_person$Group == "AI_bars" ,1, 0)
#if AI information was provied & they were placed in AI_bars condition, then 1.
```


```{r}
#removing columns that are not necessary anymore
by_person <- select(by_person, -c("Group":"Finished","PROLIFIC_PID", "exp_condition"))
```


#### Exporting cleaned *by_person averages* data set
```{r}
#6 Each observation is one person for both plants and animals
write.csv(by_person,file="Datasets/Data_cleaned_person.csv")
#Use only for t-tests and linear regressions with no mixed effects.
#This dataset will be used for the first part of the analysis.
```


```{r}
#for between-subjects correlation matrix
between_corr <- filter(by_person, AI == 1)

between_corr <- select(between_corr, c("ResponseId", "age":"Dmn_know_p_num","atn_ch" : "AI_use", "bar"))

#exporting as .csv file
write.csv(between_corr,file="Datasets/corr_csv_between.csv")
```




# #############################################################################
# #############################################################################
# _____________________________________________________________________________
### END OF CLEANING FOR PERSON DATASET - BOTH PLANTS AND ANIMALS
### EACH OBSERVATION IS ONE PERSON
# _____________________________________________________________________________
# #############################################################################
# #############################################################################




